---
title: "Yao-Chung Chen's CV"
author: Yao-Chung Chen
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: false
output:
  pagedown::html_resume:
    css: [ 'dd_cv.css', 'custom.css','resume']
    self_contained: true
#knit: pagedown::chrome_print      
---

```{r metathis, echo=FALSE}
library(metathis)
meta() %>%
  meta_name("github-repo" = "ferygood/resume") %>% 
  meta_social(
    title = "Yao-Chung Chen CV",
    description = paste(
      "CV made with the packages RMarkdown, pagedown, datadrivencv."
    ),
    url = "https://ferygood.github.io/resume/index.html",
    image = "https://ferygood.github.io/resume/img/share-card.png",
    image_alt = paste(
      "Yao-Chung Chen CV"
    ),
    og_type = "website",
    og_author = "Yao-Chung Chen",
    #twitter_card_type = "summary_large_image",
    #twitter_creator = ""
  )
```

<!-- inicio academic icons -->

<link rel="stylesheet" href="https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css"> <!-- final academic icons -->

<!-- inicio font awesome -->

```{=html}
<script src="https://kit.fontawesome.com/1f72d6921a.js" crossorigin="anonymous"></script>
```
<!-- final font awesome -->

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis',
  echo = FALSE
)
library(magrittr) # For the pipe
source("cv_printing_functions.r")
# Read in all data and initialize a CV printer object
CV <- create_CV_object(
  data_location = "https://docs.google.com/spreadsheets/d/1ZgvTp1Cxs-QASIfS7M2f3C0Vc2iU2VxnX3FLCiq6UiM/edit#gid=917338460",  
  pdf_mode = params$pdf_mode
)
CV$entries_data <- CV$entries_data %>% dplyr::filter(in_resume == TRUE)
```

```{r}
# When in pdf export mode the little dots are unaligned, so fix that with some conditional CSS.
if(params$pdf_mode) {
    cat("
<style>
:root{
  --decorator-outer-offset-left: -6.5px;
}
</style>")
}
```

# Aside

<center>![Yao-Chung Chen](https://avatars.githubusercontent.com/u/40789913?s=400&u=0b1dbe8afd40f3bcbd39a7ce3313c10ffc08fba7&v=4){width="80%" style="border-radius: 50%;"}</center>

### CONTACT

<center><a href='https://ferygood.github.io' target='_blank'><i class="fa fa-home"></i></a> <a href='https://github.com/ferygood' target='_blank'><i class="fa fa-github"></i></a> <a href='https://www.linkedin.com/in/yao-chung-chen-3a0129173/' target='_blank'><i class="fa fa-linkedin"></i></a> <a href='mailto:yaochung41@gmail.com'><i class="fa fa-envelope"></i></a> <a href='https://orcid.org/0000-0002-9927-9130' target='_blank'><i class="fab fa-orcid"></i></a></center>

<br>

I'm a Ph.D. student at [Nowick Lab](http://nowicklab.info), Freie Universität Berlin, Germany. My research focus on understanding the monoallelic expression genes in single brain neuron nuclei in Alzheimer's Disease.

### Languages

**Taiwanese Mandarin:** Native

**English:** Proficient

**German:** Beginner

<br>


# Main

## Yao-Chung Chen {#title}

## Education {data-icon="graduation-cap" data-concise="true"}

```{r}
CV %<>% print_section('education')
```


\pagebreak

::: aside
Selected activities:

### SOFTWARE

<i class="fas fa-box-open"></i> [Package {TEKRABber} - Available on Bioconductor](https://bioconductor.org/packages/release/bioc/html/TEKRABber.html) - Author.

<br>

### PROGRAMMING SKILLS

<i class="fab fa-r-project"></i> `R`

<i class="fa-brands fa-python"></i> `Python`

<i class="fab fa-markdown"></i> `RMarkdown / Quarto`

<i class="fas fa-code-branch"></i> `Git`

<i class="fab fa-github"></i> `GitHub`

:::

## Work Experience {data-icon="book"}

```{r}
CV %<>% print_section('work_experience')
```


